The ground-state energy sequences of NCSM calculations can show different convergence rates depending on the nucleus. For lighter nuclei, it is computationally feasible to calculate these energy sequences to a high value of $N_\mathrm{max}$, such that the clear convergence to the actual ground-state energy can be seen. For heavier nuclei, the extension of the model-space for NCSM calculations to a higher $N_\mathrm{max}$ results in the need of much more compuational power, since there are more possibilities to distribute the $N_\mathrm{max}$ excitation quanta to the nucleons. Therefore, NCSM calculations of heavier nuclei are restricted to model-spaces of lower $N_\mathrm{max}$, such that the resulting energy sequences won't show a satisfactory convergence to extract the exact ground-state energy of the nucleus given the used model of the interactions. For those cases, we need a ready-to-use extrapolation method, which should provide an estimate and its uncertainty of ground-state energy given those unconverged sequences.

The aim of this thesis is to provide an extrapolation framework for ground-state energy sequences resulting from NCSM calculations using neural networks. In order to use neural networks to extrapolate energies from unconverged sequences, we must first train the network on selected training data. In this chapter, we describe the whole workflow of training and evaluating a network, as well as a state-of-the-art extrapolation method using exponential function fits which will later be used to roughly assess the quality of the new extrapolation methods.

\section{Training Process}
\input{chapters/3_framework/training.tex}
\section{Evaluation Process}
\input{chapters/3_framework/evaluation.tex}
\section{Classical Extrapolation methods}
\label{sec:classical_extrapolation}
\input{chapters/3_framework/classical.tex}
